#you don't need to keep the additional writing at the top
---
title: "PSY4960- ggplot assignment"
author: "Jenna Windhorst"
date: "2022-10-29"
output: html_document
---

1. Open the starwars dataset from tidyverse
```{r}
library(tidyverse)
data("starwars")
```
#√
2.Create a graph of character's eye color. (Hint: pay attention to the class of data)
```{r}
library(dbplyr)
e=starwars %>% group_by(eye_color) %>% summarize(num=n())
ggplot(e, aes(x=eye_color,y=num,fill=eye_color))+geom_col()
```
#√- you don't need to use geom_col or summarize frequency. it's ok to do, but geom_bar in this case will give you the same graph without requiring the summarize by step
3. Customize your graph to make it more presentable (consider axes, colors, themes)
```{r}
e=starwars %>% group_by(eye_color) %>% summarize(num=n())
ggplot(e, aes(x=eye_color, y=num, fill=eye_color))+geom_point(color="skyblue")
```
#√
4. Create a graph of character's height versus mass.
```{r}
ggplot(starwars, aes(height, mass))+geom_point()
```
#√
5. Customize this graph to make it more presentable.
```{r}
ggplot(starwars, aes(height, mass))+geom_point(color="006699")
```
#√
6. Create another graph of character's height and mass. Include sex as a third variable.
```{r}
ggplot(starwars, aes(height, mass, color=sex))+geom_point()
```
#√
7. Customize this graph to make it more presentable. 
```{r}
library(RColorBrewer)
library(viridis)
ggplot(starwars, aes(height, mass, color=sex))+geom_point()+scale_color_viridis(discrete= TRUE, option="c")
```
#√
8. Make a boxplot of height. 
```{r}
ggplot(starwars, aes(height))+geom_boxplot()
```
#√
9. Make a boxplot of height for each species present in the data
```{r}
ggplot(starwars, aes(species, height))+geom_boxplot()
```
#√
10. Using any variables in the starwars dataset, create a graph that uses a color palette from viridis.
```{r}
library(viridis) #don't need to load a second time
ggplot(starwars, aes(height, mass, color=as.factor(birth_year)))+geom_point()+scale_color_viridis(discrete=TRUE, option="D")

```
#√
11.Using any variables in the starwars dataset, create a graph that uses a color palette from RColorBrewer.
```{r}
library(RColorBrewer)
ggplot(starwars, aes(height, mass, color=as.factor(skin_color)))+geom_point()+scale_color_brewer(type="seq",1,1, aesthetics = "skyblue")
```
#Don't need to load RColorBrewer a second time
12. Using any variables in the starwars dataset, create a graph using facet_wrap
```{r}
ggplot(starwars, aes(height, sex))+geom_point()+facet_wrap(~species)

```
nice job!
