1. open the mtcars dataset.
```{r}
data("mtcars")
View(mtcars)
```
2. Find the correlation between mpg and hp.
```{r}
cor(mtcars$mpg,mtcars$hp)
cor.test(mtcars$mpg,mtcars$hp)
```
3. Create a scatterplot that matches your statistic in #2. 
```{r}
library(ggplot2)
ggplot(mtcars, aes(mpg, hp)) + geom_point()+ geom_smooth(method="lm")
```
4. Find the correlation between am and mpg. Explain why you chose to use your specific function
```{r}
install.packages("ltm")
library("ltm")
biserial.cor(mtcars$mpg,mtcars$am)
Am is a categorical vairbale and mpg is numerical which is when biserial.cor test is used, a regular cor.test/cor function would not be appropriate since it is used for only numerical variables.
```
5. Run a regression to predict mpg from disp.
```{r}
lm(mpg~disp,data=mtcars)
lmmtcars<-lm(mpg~disp,data=mtcars)
```
6. Create a graph that displays your regression line. 
```{r}
lmmtcars<-lm(mpg~disp,data=mtcars)
plot(lmmtcars)
```
7. Run a t test to compare the horse power of automatic and manual transmission cars. 
```{r}
mtcars$am2<-ifelse(mtcars$am == 0, "automatic", "manual")
mtcars %>% select(am, am2)
mtcars$am2<- as.factor(mtcars$am2)
levels(mtcars$am)
t.test(mtcars$hp ~ mtcars$am2, var.equal=TRUE)
```
8. Create a graph that accompanies your statistic in #6.
```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, am2)) + geom_point()+ geom_smooth(method="lm")
```
9. Run an ANOVA to predict disp from gear. 
```{r}
lm(disp~gear,data=mtcars)
lmdg<-lm(disp~gear,data=mtcars)
summary(lmdg)
anova(lmdg)
```
10. You have a multiple choice test that is 25 questions with 5 potential options. What type of test can you run to determine if your score of 16/25 differs from chance? 
```{r}
binom.test can be used
```
11. Run the test you described in #10
```{r}
binom.test(16,25, p=.20)
```
