---
title: "Quiz 5"
author: "Jenna Windhorst"
date: "`r Sys.Date()`"
output: html_document
---

For this assignment, you should fix the code below. Knit a copy and submit the knitted version via Canvas. 

## Problem 1
```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, disp))+ geom_point() +theme_classic()
```
## Problem 2
A student is trying to make a graph that shows a regression line for weight predicted by miles per gallon with this code: 

```{r}
ggplot(mtcars,aes(wt,mpg))+geom_point()+geom_smooth(method="lm")+theme_classic()
```

## Problem 3

```{r}
data("diamonds")
diamondsDE<-diamonds %>% filter(color=="D"|color=="E")
```

## Problem 4

```{r}
time<- seq(0,60, 5)
light1<- c(0,.25,.75,2.5,3.25,5.5,5.25,8,8.88,9,9.5,9.75,9.75)
light2<- c(0,0,0,0,0,0,0,.5,1.25,2,2.75,3.75,4.25)
scientistDat<- cbind.data.frame(time,light1,light2)
ggplot(scientistDat, aes(light2,time)) + geom_point() + theme_bw()
```

## Problem 5

```{r}
lm1<- lm(light2~time+light1)
summary(lm1)
```

## Problem 6
```{r}
ggplot(mtcars, aes(hp, disp))+geom_point()
```

## Problem 7 

```{r}
data("ChickWeight")
cwwide <- pivot_wider(ChickWeight, id_cols = c("Chick", "Diet"), names_from = "Time", values_from = "weight")
```

## Problem 8

Compute the correlation between the transmission and mpg columns in the mtcars dataset.
```{r}
library("ltm")
biserial.cor(mtcars$mpg, mtcars$am)
```

## Problem 9

Color the graph using disp as a third variable. 
```{r}
ggplot(mtcars, aes(hp, mpg, color=disp))+geom_point()
```

## Problem 10

```{r}
mtcars$vs2< ifelse(mtcars$vs==0, "automatic", "manual")
```

## Problem 11
```{r}
mlinearOne <- lm(mpg~disp+wt, data=mtcars)
summary(mlinearOne)
```
## Problem 12

You volunteer at an animal shelter and play with 10 tabby cats. The veterinarian tells you that a tabby cat has a 25% chance of being born with hazel eyes. If 5 of the tabby cats you saw had hazel eyes, did this differ from chance?
```{r}
binom.test(5, 10, p=.25)
```

## Problem 13

```{r}
data("USArrests")
summary(USArrests)

USArrests$HighorLow<-NA
for(i in 1:nrow(USArrests)){
  if(USArrests$Murder[i]>8){
    USArrests$HighorLow[i]<-"high"}
  else USArrests$HighorLow[i]<-"low"
  }
```

## Problem 14

```{r}
library(car)
summary(diamonds$cut)
car::recode(diamonds$cut, '"Fair"=1; "Good"=2; "Very Good"=3; "Premium"=4; "Ideal"=5')
```

## Problem 15

4. Open the starwars dataset. Run a summary function on those that are apart of the tatooine planet. Those from Tatooine, find how many characters have a birth year of exactly or over 50. Figure out how the fix the error(s): 
```{r}
data(starwars)
view(starwars)
Tatooine <- subset(starwars, starwars$homeworld=="Tatooine")
summary(Tatooine)
TatOver50 <- Tatooine %>% filter(birth_year<=50) %>% select(sex, birth_year) 
nrow(TatOver50)
```

## Problem 16 

```{r}
data("diamonds")
diamonds$newcut<-as.numeric(diamonds$cut)
cor(diamonds$newcut, diamonds$price)
install.packages("ltm")
library("ltm")
diamonds$newcutDat<-ifelse(diamonds$newcut>3, "high","low")
biserial.cor(diamonds$price, diamonds$newcutDat)
```
## Problem 17
first, you must set your seed to the same one I do.

```{r}
set.seed(1)
```

Now that we have the same seed, we need the data to sample from

```{r}
person <- c("one","two","three","four","five","six","seven","eight","nine","ten")
favorite_number <- sample(1:1000000, 10, replace = TRUE)
animal <- c("cat","dog","axolotl")
persons_animal <- sample(animal, 10, replace = TRUE)
```

make that a data set!
```{r}
personfavAnimalDat<- cbind.data.frame(person, favorite_number, persons_animal)
```


## Problem 18

```{r}
meanSdDev<- function(col1, col2){
  mean(col1) / sd(col2)
}
```

## Problem 19
```{r}
data("ChickWeight")
ChickWeight %>% 
  filter(weight==50)
```
## Problem 20
```{r}
data("billboard")
billboardLong <- pivot_longer(billboard, cols = c(colnames(billboard[4:79])), names_to = "rankings", values_to = "weeks")
britney <- billboardLong %>% filter(artist == "Spears, Britney") %>% na.omit(rankings)
nrow(britney$rankings)
```

## Problem 21
Create a boxplot for price for the different carats
```{r}
ggplot(diamonds, aes(price, carat))+ geom_boxplot()
```
