1. Open the diamonds dataset from ggplot2.  
```{r}
library(ggplot2)
data("diamonds")
View(diamonds)
```

2. Run a correlation between the x and y variables. What do you notice? 
```{r}
cor(diamonds$x, diamonds$y)
cor.test(diamonds$x, diamonds$y)
ggplot(diamonds, aes(x, y)) + geom_point()+ geom_smooth(method="lm")
```
3. What is the correlation between price and carat?
```{r}
cor(diamonds$price, diamonds$carat)
```
4. Create a linear model predicting price from table. What is the coefficient for table? 
```{r}
lmprice.table<-lm(price~table, data=diamonds)
(summary(lmprice.table))

```
5. Run a regression and an Anova predicting price from color. What do you notice about the two types of output? 
```{r}
lm(price~color,data=diamonds)
lmOne<-lm(price~color,data=diamonds)
summary(lmOne)
anova(lmOne)

```
6. Run a t test to determine if "D" color diamonds are more expensive than "E" color diamonds. 
```{r}
ColorPrice<- diamonds %>% select(price, color)
t.test(ColorPrice$color=="D"~ColorPrice$color=="E",var.equal = TRUE, alternative="greater" )
```
7. Open the warpbreaks dataset. What test would you use to determine the correlation between wool type and breaks?
```{r}
data("warpbreaks")

```
8. What is the correlation between wool type and breaks? 
```{r}
install.packages("ltm")
library("ltm")
biserial.cor(warpbreaks$breaks,warpbreaks$wool)
```
9. A student has a 35 question, multiple choice test. Each question has 4 choices. If they answered 17 questions correctly, did their responses differ from chance?  
```{r}
binom.test(17, 35, p=.25)
```
